### 2020-04-01 PaperSDE.tex
Minor fix

\subsection{Proof of Theorem \ref{thm:mainTheorem_zetaAlpha}}
	Let us consider the decomposition \eqref{eq:alphaDecomposition}, i.e.,
	\begin{equation}
	\widehat A_k^\epl(T) = \alpha + I_1^\epl(T) - I_2^\epl(T),
	\end{equation}
	where $I_1^\epl(T)$ is defined as
	\begin{equation}
		\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
	\end{equation}
	and, by the proof of Theorem \ref{thm:mainTheorem} we have independently of $\epl$
	\begin{equation}
		\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.}
	\end{equation}
	A Taylor expansion of the first order of $V'$ yields
	\begin{equation}
	V'(Z^\epl) = V'(X^\epl) + V''(\widetilde X^\epl) (Z^\epl - X^\epl),
	\end{equation}
	where $\widetilde X^\epl$ is a random variable which assumes values between $X^\epl$ and $Z^\epl$. We can therefore write
	\begin{equation}
	\begin{aligned}
	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(X^\epl) \right ] + \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V''(\widetilde X^\epl) (Z^\epl - X^\epl) \right ] \\
	&\eqdef J_1^\epl + J_2^\epl.
	\end{aligned}
	\end{equation}
	We now consider the two terms separately and show they vanish for $\epl \to 0$. Integrating by parts in $J_1^\epl$ we obtain
	\begin{equation}
	\begin{aligned}
	J_1^\epl &= \int_\R \frac{1}{\epl} p' \left( \frac{x}{\epl} \right) V(x) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
	&= \int_\R \left ( \sigma V''(x) -  \left(V'(x) \otimes V'(x)\right) \alpha \right) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
	&= \sigma \E^{\rho^\epl} \left[ V''(X^\epl) \right] - \E^{\rho^\epl} \left[ V'(X^\epl) \otimes V'(X^\epl) \right] \alpha.
	\end{aligned}
	\end{equation}
	We then pass to the limit as $\epl \to 0$ and integrate by parts again to obtain
	\begin{equation} \label{eq:limJ1_0}
	\lim_{\epl\to 0} J_1^\epl = \sigma \E^{\rho^0} \left[ V''(X) \right] - \E^{\rho^0} \left[ V'(X) \otimes V'(X) \right] \alpha = 0.
	\end{equation}
	We now turn to $J_2^\epl$. The Hölder's inequality with conjugate exponents $p$ and $q$ and the assumptions on $p$ and $V$ yield
	\begin{equation}
	\abs{J_2^\epl} \le C \epl^{-1} \left( \E^{\rho^\epl} \abs{\widetilde X^\epl}^q \right)^{1/q} \left( \E^{\rho^\epl} \abs{Z^\epl - X^\epl}^p \right)^{1/p}.
	\end{equation}
	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, it has bounded moments by \cite[Corollary 5.4]{PaS07} and Lemma \ref{lem:bounded_momentZ}. Hence, applying Lemma \ref{lem:distanceZandX2} we have
	\begin{equation} 
	\abs{J_2^\epl} \le C \left( \delta \epl^{-2} + \delta^{1/2} \epl^{-1} \right),
	\end{equation}
	which, since $\delta = \epl^\zeta$ with $\zeta > 2$, implies
	\begin{equation}\label{eq:limJ2_0}
		\lim_{\epl \to 0} \abs{J_2^\epl} = 0.
	\end{equation}
	Finally, Lemma \ref{lem:distanceMandTildeM} and the weak convergence of the invariant measure $\phi^\epl$ to $\phi^0$ imply
	\begin{equation}
	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,
	\end{equation}
	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $J_1^\epl \to 0$ for $\epl \to 0$, which implies the desired result. \qed

>>>>

\subsection{Proof of Theorem \ref{thm:mainTheorem_zetaAlpha}}
	Let us consider the decomposition \eqref{eq:alphaDecomposition}, i.e.,
	\begin{equation}
	\widehat A_k^\epl(T) = \alpha + I_1^\epl(T) - I_2^\epl(T),
	\end{equation}
	where $I_1^\epl(T)$ is defined as
	\begin{equation}
		\lim_{T \to \infty} I_1^\epl(T) = \widetilde {\mathcal M}_\epl^{-1} \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ], \quad \text{a.s.}
	\end{equation}
	and, by the proof of Theorem \ref{thm:mainTheorem} we have independently of $\epl$
	\begin{equation}
		\lim_{T \to \infty} I_2^\epl(T) = 0, \quad \text{a.s.}
	\end{equation}
	A Taylor expansion of the first order of $V'$ yields
	\begin{equation}
	V'(Z^\epl) = V'(X^\epl) + V''(\widetilde X^\epl) (Z^\epl - X^\epl),
	\end{equation}
	where $\widetilde X^\epl$ is a random variable which assumes values between $X^\epl$ and $Z^\epl$. We can therefore write
	\begin{equation}
	\begin{aligned}
	\E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(Z^\epl) \right ] &= \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V'(X^\epl) \right ] + \E^{\rho^\epl} \left [ \frac{1}{\epl} p' \left ( \frac{X^\epl}{\epl} \right ) V''(\widetilde X^\epl) (Z^\epl - X^\epl) \right ] \\
	&\eqdef J_1^\epl + J_2^\epl.
	\end{aligned}
	\end{equation}
	We now consider the two terms separately and show they vanish for $\epl \to 0$. Integrating by parts in $J_1^\epl$ we obtain
	\begin{equation}
	\begin{aligned}
	J_1^\epl &= \int_\R \frac{1}{\epl} p' \left( \frac{x}{\epl} \right) V(x) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
	&= \int_\R \left ( \sigma V''(x) -  \left(V'(x) \otimes V'(x)\right) \alpha \right) \frac{1}{C_{\rho^\epl}} \exp \left( -\frac\alpha\sigma V(x) - \frac1\sigma p\left(\frac{x}{\epl}\right) \right) \dd x \\
	&= \sigma \E^{\rho^\epl} \left[ V''(X^\epl) \right] - \E^{\rho^\epl} \left[ V'(X^\epl) \otimes V'(X^\epl) \right] \alpha.
	\end{aligned}
	\end{equation}
	We then pass to the limit as $\epl \to 0$ and integrate by parts again to obtain
	\begin{equation} \label{eq:limJ1_0}
	\lim_{\epl\to 0} J_1^\epl = \sigma \E^{\rho^0} \left[ V''(X) \right] - \E^{\rho^0} \left[ V'(X) \otimes V'(X) \right] \alpha = 0.
	\end{equation}
	We now turn to $J_2^\epl$. The Hölder's inequality with conjugate exponents $p$ and $q$ and the assumptions on $p$ and $V$ yield
	\begin{equation}
	\abs{J_2^\epl} \le C \epl^{-1} \left( \E^{\rho^\epl} \abs{\widetilde X^\epl}^q \right)^{1/q} \left( \E^{\rho^\epl} \abs{Z^\epl - X^\epl}^p \right)^{1/p}.
	\end{equation}
	Since $\widetilde X^\epl$ assumes values between $X^\epl$ and $Z^\epl$, it has bounded moments by \cite[Corollary 5.4]{PaS07} and Lemma \ref{lem:bounded_momentZ}. Hence, applying Lemma \ref{lem:distanceZandX2} we have
	\begin{equation} 
	\abs{J_2^\epl} \le C \left( \delta \epl^{-2} + \delta^{1/2} \epl^{-1} \right),
	\end{equation}
	which, since $\delta = \epl^\zeta$ with $\zeta > 2$, implies
	\begin{equation}\label{eq:limJ2_0}
		\lim_{\epl \to 0} \abs{J_2^\epl} = 0.
	\end{equation}
	Finally, Lemma \ref{lem:distanceMandTildeM} and the weak convergence of the invariant measure $\phi^\epl$ to $\phi^0$ imply
	\begin{equation}
	\lim_{\epl \to 0} \widetilde{\mathcal M}_\epl = \mathcal M_0,
	\end{equation}
	which, together with \eqref{eq:limJ1_0}, \eqref{eq:limJ2_0} implies that $I_1^\epl(T) \to 0$ for $\epl \to 0$, which implies the desired result. \qed
